\section{S01E04 Success Perm}

\begin{multicols}{2}

\entry{perk}{振作}{v.}{Getting away from Steve and his stupid store was supposed to be one of the perks of moving here. 远离史蒂夫和他那该死的店本该是我们搬来这里的好处之一。}

\entry{perk}{小费，额外收入}{n.}{Getting away from Steve and his stupid store was supposed to be one of the perks of moving here. 远离史蒂夫和他那该死的店本该是我们搬来这里的好处之一。}

\entry{crocodile}{鳄鱼}{n.}{- I bet your husband has you living in an outhouse. - You can sleep outside, with the rest of the crocodiles. - 你老公一定让你们都住在茅厕里吧。 - 你该睡在外面，跟那些鳄鱼一起睡。}

\entry{ballers}{富豪}{n.}{They were putting up fake lemon trees all over the house, fancying up the bathroom, basically doing anything they could to look like ballers. 他们在家里放了很多假柠檬树，把浴室变得有格调，基本上是无所不用其极装成大富豪。}

\entry{defendant}{被告}{n.}{All right, the record should reflect now  that the defendant is present with counsel. 好了，记录现在可以显示被告是和律师一起的。}

\entry{tripping}{轻快的，流畅的；平稳进行的}{adj.}{Even though my parents were tripping, I was psyched. 尽管我父母很紧张，我却高兴得很。}

\entry{psych}{使精神紧张}{v.}{Even though my parents were tripping, I was psyched. 尽管我父母很紧张，我却高兴得很。}

\entry{bust}{爆裂}{v.}{Everything had to be perfect for when I busted out the new 2Pac. 我拿出全新的图派克专辑时，一切必须是完美的。}

\entry{crawl}{爬行}{v.}{Remember the time a ladybug crawled in my ear? 记得那次有只瓢虫爬进我耳朵里了吗。}

\entry{}{}{}{Well, sometimes you have to spend money you don't have, to make it seem like you have money that you don't spend. 有时候你即使没钱，也得花钱，让人觉得你其实有钱，但就是不花而已。}

\entry{prosperity}{兴旺}{n.}{In addition to fake lemon trees, another thing Chinese people did to show prosperity was get a perm. 除了假柠檬树，当年中国人喜欢做的另一件炫富的事就是烫卷发。}

\entry{pager}{寻呼机}{n.}{Oh, that's my, uh, pager. We're opening a second store. Business, right? 等下，我的传呼机响了。我们正筹划开第二家店，生意，你懂的。}

\entry{deputy}{副的}{adj. n.}{All right, deputy Jex, would you just take a step back, please? 好了，杰克斯副警长，能请你后退一步吗？}

\entry{slipper}{拖鞋}{n.}{We put on our slippers and talk about the family. We call it slipper talk. 我们会穿上拖鞋，谈论家长里短，我们称之为“拖鞋夜聊”。}

\entry{sniff}{闻}{v.}{Just because Steve and I are cushy, doesn't mean I can't sniff out a good deal. 就因为史蒂夫和我生活富足，并不代表我不知道怎么划算购物。}

\entry{condemned}{被责难的}{adj.}{Well, wait till I show her these silk throw pillows. 90\% off from a condemned hospital. 那是她没看到我这对丝绸抱枕。就1折，从停止运营的医院买来的。}

\entry{unprecedented}{前所未有的}{adj.}{Tammy's fashion hole, where they have an unprecedented selection of only left shoes. 塔米的时尚店，那里有超多的左脚单鞋卖。}



\entry{glow}{发光}{v.}{It was 60\%, and it glows in the dark, so I save money on electricity, too.}

\entry{impromptu}{事先无准备的}{adj.}{I see you've dropped by for a little impromptu dinner with the kinfolk. 我看见你带着亲戚来吃点东西啊。}

\entry{kinfolk}{亲属}{n.}{I see you've dropped by for a little impromptu dinner with the kinfolk. 我看见你带着亲戚来吃点东西啊。}

\entry{pack}{塞满}{v.}{What's going on? I told you to pack the place. 怎么回事，我叫你把餐厅弄得宾客爆满啊。}

\entry{renaissance}{文艺复兴}{n.}{Look, those are my ex-roommates, Gwendolyn and Fritz, they just came from the renaissance fair. 看，那是我的两个前室友，他们刚从文艺复兴展回来。}

\entry{howdy}{你好}{int.}{Howdy. Cattleman's Ranch. 您好，牧民的牧场餐厅。}

\entry{bummer}{懒汉}{n.}{-This roll is stupid. -Dude, why are you such a bummer? -这个花卷傻兮兮的。 -老兄，你怎么这么满腹牢骚的。}

\entry{sworn}{保证}{v.}{You know, I could have sworn you were a customer. 我敢确定你刚刚还是客人啊。}

\entry{finicky}{过分讲究的}{adj.}{You know, what we like to do is let the finicky dinners do the... Uh, Jessica, help me out here. 我们很喜欢做的一件事，让难伺候的客人去试...杰西卡，快来帮我救场。}

\entry{shaky}{不可靠的，摇晃的}{adj.}{The truth is, Cattleman's has got off to a shaky start. 真实情况是，餐厅刚营业并不顺利。}

\entry{perm}{卷发}{n.}{Now, that is a success perm. 那才叫“成功卷”呢。}

\entry{freak}{强烈反应}{v.}{Why aren't you freaking out?! 你怎么还没惊慌失措？}

\entry{coupes}{小轿车}{n.}{Sir, I've got two passions in life: law enforcement and Japanese sports coupes. 先生，我这辈子只对两件事充满激情：执法，和日产跑车。}

\entry{pantry}{食品室}{n.}{- These two were fast asleep in the backseat of a Miata I repo'd. - It was more comfortable than the pantry. - 这两个小孩子在我刚刚回收的马自达车后座睡着了。- 那里比食品室要舒服多了。}

\entry{dibs}{权力，零钱}{n.}{As well as dibs on anything we find in the cars. 在车里发现的东西，也都归我们。}

\entry{swampland}{沼泽}{n.}{Well, I can't wait to get out of this swampland. 我真是迫不及待要离开这个沼泽了。}





\end{multicols}