\section{S01E05 Persistent Romeo}

\begin{multicols}{2}

\entry{cereal}{麦片}{n.}{- Man, we ate so much cereal. - Yeah, we did. Remember when Doug wet the  bed? - 天啊，我们吃了太多的麦片。- 是啊，没错，记得道格尿床那事吗。}

\entry{sploosh}{四处飞溅}{v.}{- Yeah, we did. Remember when Doug wet the  bed? - Sploosh! - 是啊，没错，记得道格尿床那事吗。- 狂喷啊！}

\entry{corny}{过时的}{adj.}{Sleepovers are corny as hell. 在同学家过夜真老套俗气。}

\entry{scout}{童子军}{n.}{He's on an eagle scout's trip until Sunday, so it's all ours. 他会在鹰级童子军一支训练到周日，所以我们可以尽情享用。}

\entry{pedophile}{恋童癖}{n.}{- Why not? It's just a sleep over. Because pedophiles. - I saw it on the Nightly News. - 为什么不行？就是过夜而已。- 因为要防恋童癖。我在《夜间新闻》上看到的。}

\entry{rape}{强奸}{v.}{Are you at risk for date rape? 你会面临约会时被强奸的危险吗？}

\entry{couch}{沙发}{n.}{Are deadly chemicals in your couch? 你的沙发里含有致命化学品吗？}

\entry{harassment}{骚扰}{n.}{Sexual harassment in the workplace. 工作场所的性骚扰。}

\entry{monger}{传播；贩子}{n. v.}{Fearmongering was made for my mom, and her paranoia made the rest of us miserable. 我妈就喜欢信这些制造恐慌的消息，她的偏执妄想症让我们大家苦不堪言。}

\entry{paranoia}{妄想症}{n.}{Fearmongering was made for my mom, and her paranoia made the rest of us miserable. 我妈就喜欢信这些制造恐慌的消息，她的偏执妄想症让我们大家苦不堪言。}

\entry{overreach}{因过于雄心勃勃而失败}{v.}{I overreached. I see that now. 我做做过头了，我现在明白了。}

\entry{frivolous}{不重要的；不重要}{adj. n.}{We don't want to be a target for frivolous lawsuits. 我们不会希望因为鸡毛蒜皮的小争端被告的。}

\entry{grievances}{不满}{n.}{At my family's furniture store, I handled employee grievances. 在我们家族的家具店，我就是处理员工不满的。}

\entry{flirting}{调情（的）}{n. v. adj.}{To make sure we always have a pleasant work environment, flirting should be avoided at all times. 为了确保能有一个愉悦的工作环境，调情是严格禁止的。}

\entry{fig}{无花果}{n.}{Help yourselves to fig Newtons and milk. 我们准备了无花果馅饼和牛奶，你们随意吃。}

\entry{}{}{undefined}{To make some friends, I had to break some rules, and your boy was willing to do whatever it took. 为了交朋友，我只能打破规矩了。本少爷真是不择手段达成目标。}

\entry{butt}{屁股}{n.}{I'll draw butts on your homework. 那我就在你的家庭作业上画满屁股。}

\entry{raisin}{葡萄干}{n.}{Raisins! Raisins! They used to be grapes! 葡萄干，葡萄干，以前是葡萄。}

\entry{plea}{请愿；借口}{n.}{I was a repeat sexual harassment offender who, thanks to a complicated plea deal, is now working for the good guys. 我曾经是个多次犯案的性骚扰者，多亏了复杂的认罪协议，现在开始为好人工作了。}

\entry{fondling}{被溺爱的人}{n.}{No one is fond of fondling. 没人喜欢被摸。}

\entry{squid}{鱿鱼}{n.}{These are the snacks you got me for my sleepover?  Squiddies? What are squiddies? 这就是你为我的过夜派对准备的零食吗？乌贼片？什么鬼东西啊。}

\entry{octopus}{章鱼}{n.}{They were on sale, and there's a funny octopus on the bag. 刚好在打折而已，包装袋上还有个很逗的小章鱼呢。}

\entry{squirt}{喷射}{n. v.}{Who's squirting ink on a dog. 它正往小狗身上喷墨汁呢。}

\entry{stew}{炖汤}{n. v.}{There's pork bone stew on the stove. 炉子上有一锅骨头汤。}

\entry{crooner}{低声唱歌的人或歌手}{n.}{Then there's "the crooner". 此人是“情歌哥”。}

\entry{tempting}{吸引人的（地）}{adj. adv.}{And watch out for "tempting Tanya." 当心”诱惑坦娅“。}

\entry{ensnare}{诱捕}{v.}{She'll use her sexuality to ensnare you. 她会用她的性魅力诱惑你。}

\entry{blade}{刀片}{n.}{My wife worries about sexual harassment, baby thieves, my favorite blue sweater getting me mistaken for a gang member. 我老婆闲的没事却会担心性骚扰，苹果里的刀片，拐卖儿童贩，以及我最爱的蓝色毛衣会让我被误认为是黑帮成员。}

\entry{bluff}{吓唬}{n. v.}{You're bluffing. You don't have it. 你在诈我，你根本没有大牌在手。}

\entry{monologue}{独白}{n.}{And most importantly, like we always say during the "S.N.L" monologue when a musician hosts, wrap it up. 最重要的是，就像一个音乐人主持《周六夜现场》时，多穿点。}

\entry{stir}{激动}{n.}{I'm in the house all day, and it's making me stir-crazy. 我整天都只能待在家里，那快把我逼疯了。}


\end{multicols}

