\section{S01E06 Fajita Man}

\begin{multicols}{2}

\entry{phantom}{幻影；幻觉的}{n. adj.}{I feel phantom flicks. 我感觉到”幻影弹指“了。}

\entry{loiter}{磨蹭}{v.}{You really can't loiter in the frozen food aside. 你们不能在冷冻食品通道赖着不走。}

\entry{prominent}{突出的；杰出的}{adj.}{Who do you think we are, the Chians? Very prominent family in D.C. 你以为我们是蒋氏家族吗，那是华盛顿特区的豪门贵族。}

\entry{upholstery}{家具装饰业}{n.}{They're sort of the Liaos of the upholstery world. 他们就相当于室内装潢界的廖氏家族。}

\entry{textile}{纺织品}{n.}{They made their fortune in textiles. 他们主要是靠纺织品发财的。}

\entry{mow}{割草}{n. v.}{I've been double mowing the Millers' lawn. 我把米勒家的草坪割了两次。}

\entry{karate}{空手道}{n.}{So a basketball man made a video game about karate'ing people? 一个打篮球的做了个电子游戏，是关于用空手道制服别人的？}

\entry{stunt}{绝技；表演特技}{n. v.}{This wasn't the first time pops had come home excited about a "Winning" Publicity stunt. 这已经不是我爸第一次兴冲冲地回到家说自己想到一个致胜的促销活动。}

\entry{lest}{以免}{conj.}{Lest there be claims of copyright plunder, that‘s b-o-o-k. 为免版权上的争端，那是书的拼音。}

\entry{plunder}{掠夺；赃物}{n. v.}{Lest there be claims of copyright plunder, that‘s b-o-o-k.  为免版权上的争端，那是书的拼音。}

\entry{stumble}{绊脚}{n. v.}{Luckily, my dad was about to stumble into the biggest restaurant craze of the mid '90s. 幸运的是，我爸即将赶上餐厅业在90年代中期最大的浪潮。}

\entry{skillet}{煎锅}{n.}{Orlando can't get enough utility-grade skirt steak delivered in a sizzling skillet. 奥兰多人永远吃不够可用食材级别的横肌牛肉用滋滋的铁板端上去。}

\entry{tortillas}{玉米薄饼}{n.}{You bring them tortillas, veggies, and steak, and they assemble it themselves. 你端上玉米薄饼，蔬菜和牛排，他们自己组合在一起。}

\entry{edible}{可食用的；食品}{adj. n.}{It's like an edible Ikea chair. 那就像是可以吃的宜家椅子。}

\entry{swole}{健美的}{adj.}{Papa, you been working out? ’Cause you're looking swole. 爸爸，你最近有健身吗？因为你看起来很健美。}

\entry{bunk}{床位}{n.}{I guess I just have to share a bunk bed with a total stranger. 大概我得和一个完全陌生的人共享上下铺了、}

\entry{tend}{照料}{v.}{You know, rather than have my 11-year-old tend bar, I thought you could work the floor. 我觉得11岁的你负责吧台不合适，我想的是让你当个打杂的。}

\entry{dope}{酷毙了}{n.}{Aw, dope! Like manage the servers? 棒极了，比如管理服务员吗？}

\entry{hedge}{树篱}{n. v.}{Did a third hedge trimming at the Millers. 我第三次修剪了米勒家的草坪。}

\entry{hustle}{拼命}{v. n.}{Me? I'm hustlin' for that money. 至于我，我在拼了小命赚钱。}

\entry{moler}{臼齿}{n.}{I gave my sister a candy apple, and her last molar came out. 我给了我妹妹一个冰糖苹果，她最后一颗臼齿就啃掉了。}

\entry{rage}{愤怒}{n. v.}{It's hot at raging waters, too. 狂潮水上乐园的水也是热的。}

\entry{blimped}{软式小型飞船，肥胖的人}{n.}{I think Andrew left her because she blimped out. 我觉得安德鲁离开她是因为她肥成猪了。}

\entry{dock}{剪短}{v.}{Oh, sorry, Eddie, but I had to dock your pay for all the food you dropped. the plates you broke. 抱歉，埃迪，我必须扣掉你一部分工资因为你撒落了一些食物，打碎了一些盘子。}

\entry{contender}{竞争者}{n.}{- Excuse me. Are you interested in this house? Because... - Yes, very. Definitely a contender. - 打扰一下，你对这房子到底有没有兴趣，因为... - 是的，很感兴趣，绝对是候选买家。}

\entry{lousy}{极坏的}{adj.}{- We can always change the paint. - But not the lousy school district. - 我们是可以换掉油漆颜色的。- 但这里的烂学区可换不掉。}

\entry{cemetery}{墓地}{n.}{- The skylights should help the resale. - But the cemetery down the street won't. - 天窗会有助于再出售。- 但街尾那个墓地只会令人望而却步。}

\entry{spill}{溢出；使溢出}{v. n.}{He didn't show up for work today. Nancy had to cover for him, and she spilled salsa all over Regina Snipes! 他今天没去餐厅工作，南兮不得不代替他上阵。她把莎莎酱泼了她一身。}

\entry{countertop}{（厨房的）工作台面}{n.}{With this countertops? How could you not be? 爱上这桌面了吗？怎么会不惹人喜爱呢。}

\entry{granite}{花岗岩}{n.}{Granite throughout. 全材质花岗岩。}

\entry{realtor}{房产经纪人}{n.}{I just sold a house! I am a realtor now! 我刚卖掉一栋房子，我现在是房产经纪人了。}

\entry{infertility}{不肥沃}{n.}{Also, I found out what ruined the Millers' marriage. Male infertility. 并且，我还发现了真正让米勒夫妇婚姻玩完的原因。男性不育症。}

\entry{crank}{曲柄；装曲柄}{n. v.}{Crank up the a/c to "Low". 把空调开到最低温。}

\entry{estate}{财产；房地产；身份}{n.}{A real estate pimp! 房产经纪人。}


\end{multicols}