\section{S01E07 Shutdown At The Golden Saddle}

\begin{multicols}{2}

\entry{billboard}{广告牌}{n.}{Well, I'm setting the scene, building suspense for when you guys see the restaurant billboard. 我是在构建一个情境，为你们待会儿见到餐厅广告牌制造一点悬念。}

\entry{beefy}{健壮的}{adj.}{No, you are a beefy lake-house owner. 不，你是个壮实的湖边小屋房主}

\entry{butler}{男管家}{n.}{I'm not the butler, I'lI cut ya, headbutt ya. 我不是伺候你的，我会砍死你、撞死你。}

\entry{tattle}{闲聊}{n. v.}{- Mom, Eddie's rapping at my Always-there bear. - Did they give you that pin for narc-ing? - No, that's tattle-turtle. - 妈，埃迪在对我的"全勤熊”唱饶舌乐。- 那个小熊是他们奖励你打小报告的吗？- 不，那是闲聊龟。}

\entry{stale}{不新鲜的；变陈旧}{adj. v.}{She was as tough as a stale tootsie roll, and I loved it. 她对我的态度冷得跟冰一样，但我就喜欢这样的。}

\entry{chamber}{会所；室内的；关在室内}{n. adj. v.}{And we have been invited to the chamber of commerce charity-fundraising event. 而且我们还获邀参加商会举办的慈善筹款活动。}

\entry{wreck}{失事；破坏}{n. v.}{Check yo self before you wreck yo self. 在毀掉自己之前 最好先搞清楚。}

\entry{carpool}{拼车}{v.}{Thanks. See you in carpool tomorrow, Mrs. Wilson. 谢谢，明天拼车时再见，威尔逊太太。}

\entry{burrito}{玉米卷}{n.}{My bus friends already miss me, so they dropped off this breakfast burrito. 我的校车同伴已经开始想我了，所以他们把这个早餐玉米卷送到了家门口。}

\entry{glistening}{闪耀的}{adj.}{I want to see the billboard glistening in the morning dew. 我想看看广告牌在清晨的露水中发光的样子。}

\entry{dew}{露水；结露水；露水弄湿}{n. v.}{I want to see the billboard glistening in the morning dew. 我想看看广告牌在清晨的露水中发光的样子。}

\entry{anatomically}{在解剖学上}{adv.}{This is anatomically impossible. 那在解剖学上来说就是不可能的}

\entry{teat}{奶头}{n.}{Everybody know you got to squeeze the teat to produce the milk. 是个人都知道，你得用劲去挤奶头才能挤出牛奶。}

\entry{thermometer}{温度计}{n.}{They should all be in bed by 9:00, and if anyone feels warm, there's a thermometer and flintstones chewables. 他们9点必须上床睡觉，如果有谁觉得发热，家里有体温计和维生素片。}

\entry{visionary}{有远见的（人）}{adj. n.}{You are a visionary. 你是个有远见的人。}


\entry{knockoff}{仿制品}{n.}{Cattleman's Ranch was a total knockoff of Golden Saddle. 牧民的牧场餐厅完全是金马鞍餐厅的仿制品。}

\entry{franchise}{参政权；出售特许权}{n. v.}{And that's what you get when you buy a Golden Saddle franchise. 等你们买下金马鞍餐厅的加盟权，就能得到那个。}

\entry{cherish}{珍爱}{v.}{但童年消失得很快，我努力去珍惜。 But it goes so fast. I try to cherish it.}

\entry{buckle}{扣；扣住}{n. v.}{And to size you for your belt buckles! 然后量下你们的腰围，用来做皮带扣。}

\entry{bounce}{弹力；弹起}{n. v.}{You added a salad bar, you have "wanted" posters for people who bounce checks, and the bears aren't even the same color. 你添加了一个沙拉吧，你还搞了通缉令，挂着那些逃单的客人，并且熊的颜色根本不一样啊。}

\entry{vandalize}{破坏}{v.}{If you think stealing our employee, and vandalizing our billboard is gonna make us back down, you are wrong. 如果你觉得挖走我们的雇员，破坏我们的广告牌就能逼我们放弃，那你就错了。}


\end{multicols}