\section{S01E08 Phillip Goldstein}

\begin{multicols}{2}

\entry{jib}{停止不动；船首三角帆}{v. n.}{Obviously, you've never tried to raise the jib on wet teak. 显然，你从末试过在潮湿船板上升过帆。}

\entry{cop}{警察}{n.}{Okay, Louis, I know you like to be good cop, but somebody has to wield the hammer in this family. 好吧，路易斯，我知道你喜欢当好人，但家里总得有个当恶人的。}

\entry{wield}{挥舞；行使}{v.}{Okay, Louis, I know you like to be good cop, but somebody has to wield the hammer in this family. 好吧，路易斯，我知道你喜欢当好人，但家里总得有个当恶人的。}

\entry{cape}{披风}{n.}{Letting the rest flap out like a cape. 下面像个披风似的随风摆动。}

\entry{scrabble}{乱摸}{n. v.}{Why do you want to be a letter that's only worth two points in scrabble?! 你为什么会想当一个在填宇游戏里只值两分的字母？}

\entry{lateral}{侧面（的）}{n. adj.}{Mitch has decided to take a lateral position at the Golden Saddle. 米奇已经决定去金马鞍餐厅谋高就了。}

\entry{mutual}{相互的}{adj.}{I feel like you have mutual interests and experiences. 我觉得你们有共同的兴趣和经历。}

\entry{repulsive}{令人厌恶的}{adj.}{Stinky tofu sounds repulsive. 臭豆腐听上去好恶心。}

\entry{pun}{双关话；说双关话}{n. v.}{The pun gun is set to laughs. 那个双关语就是引人发笑啊。}

\entry{commence}{（使）开始}{v.}{In response to complaints of racism, I now commence the first meeting of the... Pacific Rim Club. 为了回应种族岐视的指控，我现在宣布召开环太平洋俱乐部第一次会议。}

\entry{rim}{边；做...的边}{n. v.}{In response to complaints of racism, I now commence the first meeting of the... Pacific Rim Club. 为了回应种族岐视的指控，我现在宣布召开环太平洋俱乐部第一次会议。}

\entry{parchment}{羊皮纸}{n.}{I'm leaving you a box of watercolors and parchment if you choose to express yourself through monumental landscape painting. 我甚至给你们准备了一盒水彩和仿羊皮纸，如果你们想通过画风景画来表达内心情感的话。}

\entry{monumental}{雄伟的}{adj.}{I'm leaving you a box of watercolors and parchment if you choose to express yourself through monumental landscape painting. 我甚至给你们准备了一盒水彩和仿羊皮纸，如果你们想通过画风景画来表达内心情感的话。}

\entry{stint}{节约}{n. v.}{After that, I did a four-year stint maitre'd in' at Spay-go. 然后 我又当了4年的餐厅领班。}

\entry{wobbler}{动摇的人}{n.}{Noticed a couple wobblers over there, so I balanced 'em out with some scrap wood. 我注意到那边的桌椅有些晃动，所以我用木头边角料给弄平衡了。}

\entry{scrap}{小块；废弃}{n. v.}{Noticed a couple wobblers over there, so I balanced 'em out with some scrap wood. 我注意到那边的桌椅有些晃动，所以我用木头边角料给弄平衡了。}

\entry{petition}{请愿；请愿书}{n. v.}{Eddie, will you sign this petition? 埃迪，你愿意在这个请愿书上签名吗？}

\entry{confrontational}{对抗的}{adj.}{It's just that you're so naturally confrontational. 只是因为你天生处于战斗模式中。}

\entry{matinee}{音乐会}{n.}{1'I go to your silly rap show tomorrow night if you bring me to a matinee performance of "Les Miserables" earlier that day. 我明晚可以陪你去听那傻兮兮的演唱会，前提是你答应带我去看当天早些时候的《悲惨世界》的演出。}

\entry{sloppy}{邋遢的；粗心}{adj. n.}{Sloppy. For "Les Mis," You're gonna want to clean this up. 邋遢，要看高雅的《悲惨世界》，你必须清理干净。}

\entry{mezzanine}{包厢}{n.}{God, I love the mezzanine. 天啊，我好爱这个包厢。}

\entry{gorgeous}{极好的}{adj.}{So, I bought this gorgeous shirt myself. 所以我就自己买了这件超棒的纪念衫。}

\entry{philistine}{下里巴人（的）}{n. adj.}{You're a philistine, Huang. 你是个没教养的人，黄。}

\entry{dimple}{酒窝；出现酒窝}{n. v.}{I couldn't fire him. Those dimples. 我没办法开除他，那小酒窝太可爱了。}


    
\end{multicols}