\section{S01E09 License To Sell}

\begin{multicols}{2}

\entry{swoop}{俯冲}{v. n.}{Oh, she's the one who keeps swooping in on my listings! 她她就是那个一直暗中对我清单上的房子下手的人。}

\entry{caricature}{讽刺画}{n. v. adj.}{We have a caricature of him on the wall. 我们的墙上还有一幅他的讽刺画呢。}

\entry{apron}{围裙}{n.}{I'm wearing an apron, standing next to a barbecue. 我穿着围裙，站在烧烤设备旁边。}

\entry{omnidirectional}{全方向的}{adj.}{That's what the Philippe Monday 3000s provides... a cone of premium, omnidirectional hot air for that all-over dry. 那正是菲利普周一3000干发机具备的，一个半球形罩子，全方位热风，让头发全面风干。}

\entry{jive}{假的；哄骗}{adj. v.}{You jive. 你开玩笑吧。}

\entry{freak}{怪物；怪事；有怪癖的人}{n.}{But I'm kind of a freak of nature. 但我就是业内奇葩。}

\entry{sentinel}{哨兵；放哨}{n. v.}{I've been voted top-selling realtor five years running according to the Orlando Sentinel. 我已经连续5年被选为最出色的房产经纪人了，《奥兰多前哨报》评的。}

\entry{detention}{扣留}{n.}{You are gonna spend the rest of your life in detention. 你的余生都要被留堂了。}

\entry{rebel}{叛逆者；造反}{n. v.}{Looks like we're just two rebels here. 似乎我们是两个不羁的少男少女啊。}

\entry{weed}{铲除；杂草}{v. n.}{Like you said, got to weed out the dum-dums. 就像你说的，要把那些笨蛋都淘汰。}

\entry{stance}{姿态}{n.}{Excuse the 3000s. She got a wider stance than I realized. 请原谅这机器，它比我原来以为的要占地方一些。}

\entry{condo}{公寓}{n.}{Oh, yes, a lot of showings today. Busy, busy. Houses, mansions, condos, houseboats. 是啊，要参观好多房子，忙啊，忙啊。带院房，庄园，公寓，船屋。}

\entry{turd}{可鄙的人}{n.}{Okay, you little turds. 好了，你们这帮小免崽子。}

\entry{crow}{乌鸦；啼叫}{n. v.}{You ever seen "The crow"? lt's one of my favorite movies. 你看过《乌鸦》吗？那是我最爱的电影之一。}

\entry{maniac}{疯子；狂热的}{n. adj.}{Well, I can't go outside, because my friend is a jogging maniac. 我不能出去，因为我的朋友是个慢跑狂}

\entry{leprechaun}{妖精}{n.}{Let's see what you have in your pot, you cute, little leprechaun. 来看看奖项结果吧，你个可爱的小妖精。}

\entry{lieutenant}{中尉}{n.}{Damn it, lieutenant! The shields are down! 该死的，中尉，防护盾已被击垮。}

\entry{crimp}{卷发}{n. v.}{And this is my crimper with interchangeable plates. 这是我的卷发器，有可替换的金属板。}

\entry{crib}{小床}{n.}{I was in her crib! 我进入她房里了啊。}

\entry{pierce}{刺入}{v.}{What I really need to learn is ear piercing. 我真正需要学习的，是打耳洞。}

\entry{propensity}{倾向}{n.}{Quick... "Propensity." 速问速答，“倾向”的拼法。}

\entry{legit}{合法的}{adj.}{You're legit now. 你现在合法了啊。}

\entry{propane}{丙烷}{n.}{He's getting his propane tank fixed. 他正在找人修理他的燃料罐。}

\entry{stencil}{蜡纸；模板；用蜡纸印刷}{n. v.}{Hey, Eddie! I just found my henna stencils. 嘿，埃迪，我刚找到我的指甲燃料板。}

\entry{mustard}{芥末}{n.}{It was just some big black ouy in a mustard-colored suit. 那只是个普通的黑人，穿着青黄色的西装而己。}


\end{multicols}