\section{S01E10 Blind Spot}

\begin{multicols}{2}

\entry{swoop}{俯冲}{v. n.}{Oh, she's the one who keeps swooping in on my listings! 她她就是那个一直暗中对我清单上的房子下手的人。}

\entry{caricature}{讽刺画}{n. v. adj.}{We have a caricature of him on the wall. 我们的墙上还有一幅他的讽刺画呢。}

\entry{apron}{围裙}{n.}{I'm wearing an apron, standing next to a barbecue. 我穿着围裙，站在烧烤设备旁边。}

\entry{omnidirectional}{全方向的}{adj.}{That's what the Philippe Monday 3000s provides... a cone of premium, omnidirectional hot air for that all-over dry. 那正是菲利普周一3000干发机具备的，一个半球形罩子，全方位热风，让头发全面风干。}

\entry{jive}{假的；哄骗}{adj. v.}{You jive. 你开玩笑吧。}

\entry{freak}{怪物；怪事；有怪癖的人}{n.}{But I'm kind of a freak of nature. 但我就是业内奇葩。}

\entry{sentinel}{哨兵；放哨}{n. v.}{I've been voted top-selling realtor five years running according to the Orlando Sentinel. 我已经连续5年被选为最出色的房产经纪人了，《奥兰多前哨报》评的。}

\entry{detention}{扣留}{n.}{You are gonna spend the rest of your life in detention. 你的余生都要被留堂了。}

\entry{rebel}{叛逆者；造反}{n. v.}{Looks like we're just two rebels here. 似乎我们是两个不羁的少男少女啊。}

\entry{weed}{铲除；杂草}{v. n.}{Like you said, got to weed out the dum-dums. 就像你说的，要把那些笨蛋都淘汰。}

\entry{stance}{姿态}{n.}{Excuse the 3000s. She got a wider stance than I realized. 请原谅这机器，它比我原来以为的要占地方一些。}

\entry{condo}{公寓}{n.}{Oh, yes, a lot of showings today. Busy, busy. Houses, mansions, condos, houseboats. 是啊，要参观好多房子，忙啊，忙啊。带院房，庄园，公寓，船屋。}

\entry{turd}{可鄙的人}{n.}{Okay, you little turds. 好了，你们这帮小免崽子。}

\entry{crow}{乌鸦；啼叫}{n. v.}{You ever seen "The crow"? lt's one of my favorite movies. 你看过《乌鸦》吗？那是我最爱的电影之一。}

\entry{maniac}{疯子；狂热的}{n. adj.}{Well, I can't go outside, because my friend is a jogging maniac. 我不能出去，因为我的朋友是个慢跑狂}

\entry{leprechaun}{妖精}{n.}{Let's see what you have in your pot, you cute, little leprechaun. 来看看奖项结果吧，你个可爱的小妖精。}

\entry{lieutenant}{中尉}{n.}{Damn it, lieutenant! The shields are down! 该死的，中尉，防护盾已被击垮。}

\entry{crimp}{卷发}{n. v.}{And this is my crimper with interchangeable plates. 这是我的卷发器，有可替换的金属板。}

\entry{crib}{小床}{n.}{I was in her crib! 我进入她房里了啊。}

\entry{pierce}{刺入}{v.}{What I really need to learn is ear piercing. 我真正需要学习的，是打耳洞。}

\entry{propensity}{倾向}{n.}{Quick... "Propensity." 速问速答，“倾向”的拼法。}

\entry{legit}{合法的}{adj.}{You're legit now. 你现在合法了啊。}

\entry{propane}{丙烷}{n.}{He's getting his propane tank fixed. 他正在找人修理他的燃料罐。}

\entry{stencil}{蜡纸；模板；用蜡纸印刷}{n. v.}{Hey, Eddie! I just found my henna stencils. 嘿，埃迪，我刚找到我的指甲燃料板。}

\entry{mustard}{芥末}{n.}{It was just some big black ouy in a mustard-colored suit. 那只是个普通的黑人，穿着青黄色的西装而己。}

\entry{cutthroat}{不公正的}{adj.}{And with every grade competing, and a pizza party on the line for the winner, even the nice kids got cutthroat. 由于每个年级都要参加比赛，赢家可以去参加披萨派对，即使是乖宝宝也会变得极具攻击性。}

\entry{aquarium}{鱼缸；水族馆}{n.}{I would have him stay on the sofa bed, but Eddie spilled oyster sauce on it, so now it smells like an aquarium. 我也想让他直接睡沙发床，但是埃迪把牡蛎酱洒在上面了，所以现在那沙发闻起来跟水族馆一样。}

\entry{quarantine}{隔离}{n. v.}{So everybody out. Grandma's room is now a quarantine zone. 大家都出去吧，奶奶的房问现在是隔离区了。}

\entry{contagious}{有传染病的}{adj.}{And stay away from Evan because he is contagious. 另外，远离埃文，因为他是传染源。}

\entry{massage}{马杀鸡}{n.}{Well, maybe we'll go for massages afterwards. 或许我们逛完了会去按个摩什么的。}

\entry{scaffold}{脚手架}{n.}{Did somebody say "Croquembouche"? The sugar is the scaffolding. 刚刚是有人说焦糖奶油松饼吗？糖分堆积起来的哦。}

\entry{chime}{鸣响；钟声}{v. n.}{I don't know if boys are still into wind chimes these days, but I hope their gentle tinklings will always remind you of home. 我不知道现在的男孩还喜不喜欢风铃，但我希望它们轻柔的撞击声总能让你想到家。}

\entry{attentive}{体贴的}{adj.}{So attentive. 无微不至。}

\entry{auditioning}{试音}{n. v.}{I'm auditioning for the "Aladdin" ice show spectacular. 我来参加《阿拉丁》 冰上秀的海选。}

\entry{spectacular}{壮观的}{adj.}{I'm auditioning for the "Aladdin" ice show spectacular. 我来参加《阿拉丁》 冰上秀的海选。}

\entry{penthouse}{阁楼}{n.}{You cant plant me in your penthouse. “你无法把我当花草 种在你的阁楼”。}

\entry{plough}{犁地}{v. n.}{I'm going back to my plough. 我要回到乡下犁田去。}

\entry{germ}{细菌；胚芽；萌芽}{n. v.}{Besides, I'm saving my germs for someone else. 再说了，我得留着我的病菌传染给另一个人。}

\entry{robe}{睡袍；穿上睡袍}{n.}{I hope you don't mind that I borrowed this robe. 我希望你不介意我借穿下你的浴袍。}

\entry{oatmeal}{燕麦片}{n.}{Evan! I made you an oatmeal bath! 埃文，我给你做了燕麦片。}

\entry{crust}{坚硬外皮；结硬皮}{n. v.}{Okay, so you know how the earth's crust is broken up into 17 tectonic... 好的，你知道地壳分成了17块…}

\entry{tectonic}{构造的，建筑的}{adj.}{Okay, so you know how the earth's crust is broken up into 17 tectonic... 好的，你知道地壳分成了17块…}

\entry{incubation}{孵化；潜伏期}{n.}{The incubation period for chickenpox is at least 48 hours. 水痘的潜伏期至少要48小时。}

\entry{rash}{疹子；鲁莽的}{n. adj.}{I should be covered in a skin rash that starts at my torso and works its way down to my limbs in a period of three to seven days. 我会浑身起皮疹，先从躯干部位开始，然后传到四肢，大约会持续3到7天。}

\entry{torso}{躯干}{n.}{I should be covered in a skin rash that starts at my torso and works its way down to my limbs in a period of three to seven days. 我会浑身起皮疹，先从躯干部位开始，然后传到四肢，大约会持续3到7天。}

\entry{varicella}{水痘}{n.}{Damn you, varicella zoster virus! 该死的水痘带状疱疹病毒。}

\entry{zoster}{带状疱疹}{n.}{Damn you, varicella zoster virus! 该死的水痘带状疱疹病毒。}

\entry{rub}{摩擦}{v. n.}{The old Huang fire rub. 黄氏祖传火揉大法。}

\entry{pastry}{糕点}{n.}{He's out there, and I'm jealous of all the delicious French pastries that guy has in his future. 那个人一定存在，我很嫉妒他将来可以吃到那么多好吃的法式馅饼。}

\entry{sperm}{精液}{n.}{These two sperm bags giving you any trouble? 那两个精囊找你麻烦了吗？}

\entry{crystal}{水晶；水晶的}{n. adj.}{When I'm way up here, it's crystal clear. 当我在这高空，一切都非常清晰明了。}


\end{multicols}