\section{S01E11 Very Superstitious}

\begin{multicols}{2}

\entry{rodent}{啮齿动物}{n.}{- It has a rodent problem. - It's pet-friendly. - 里面有啮齿动物。 - 说明适合养宠物。}

\entry{flier}{传单}{n.}{I don't want to be in the same room as that flier. 我不想跟那些传单待在同一个房间里。}

\entry{sewer}{下水道；裁缝师}{n.}{You mean those karate frogs who eat pizza in a sewer? 你是说那些打空手道，在下水道吃披萨的青蛙吗。}

\entry{jade}{翡翠}{n.}{She thinks jade wards off evil spirits. 她觉得玉能辟邪。}

\entry{ward}{避开；保卫}{v. n.}{She thinks jade wards off evil spirits. 她觉得玉能辟邪。}

\entry{dub}{配音；轻点；鼓声}{v. n.}{Dubbed straight from the radio. Five bucks makes it happen. 直接从收音机录的，只卖5美金。}

\entry{squash}{南瓜}{n.}{Am I selling squash? Get outta here, haggle-puss! 我卖的是南瓜吗，滚吧，砍价娘们。}

\entry{bootleg}{非法制造或贩卖（的）}{v. adj.}{Are you selling bootleg CDs? 你是在卖盗版CD吗。}

\entry{counselor}{顾问}{n.}{And I'm not a teacher, I'm a counselor. 我不是老师，我是个辅导员。}

\entry{hustle}{催促}{v. n.}{But I am about you channeling that hustle into something more positive. 但我需要你把你这干劲转移到更积极的事情上来。}

\entry{husky}{强健的（人）}{adj. n.}{You got an everyman's husky build... and a middle-class background, so people can relate to you. 你有一般人的强健体格，中产阶级背景，大家对你比较有亲切感。}

\entry{dreidel}{陀螺}{n.}{Cool. Chocolate dreidels. 好棒，有巧克力陀螺。}

\entry{ballot}{选票；选举}{n. v.}{Don't leave your ballot Blanka. 别让你的选票"空白"哦。}

\entry{liquor}{酒；喝酒}{n. v.}{Ashley Alexander bought me a bottle of champagne to celebrate. I took it back to the liquor store... bought nine Snickers and a Crystal Pepsi. 艾什莉·亚历山大给我买了一瓶香槟庆祝，我拿回酒水店，换了九条士力架和一瓶水晶百事。}

\entry{commission}{佣金；委托}{n. v.}{- I already got my commission check. - Great. - 我已经拿到我的佣金了。 -太好了。}

\entry{pedicure}{修脚；修脚师}{n.}{I'm gonna treat myself to a pedicure done by a white lady. 我要让白人女给我修脚来犒劳我自己。}

\entry{tainted}{污染的}{adj.}{No, we can't! It's tainted! 不行，这钱已经被污染了。}

\entry{clam}{蚌；蛤；挖蛤}{n. v.}{Do you think it'd be gross to dip this in clam chowder? 你觉得这个蘸蛤蜊浓汤吃会不会很恶心。}

\entry{chowder}{海鲜浓汤}{n.}{Do you think it'd be gross to dip this in clam chowder? 你觉得这个蘸蛤蜊浓汤吃会不会很恶心。}

\entry{cord}{绳索；捆绑}{n. v.}{Hey, boys, we can't let Mom know Eddie tripped over the cord of the mechanical bull and broke his arm. 小子们，我们不能让老妈知道埃迪被机械牛的电线绊倒导致摔断了手。}

\entry{crotch}{胯部}{n.}{Do I tell her it looks like her body's half crotch? 我能告诉她身体像是被分成了两半吗}

\entry{rug}{毛毯}{n.}{And then he tripped on a rug and fell. 他被毛毯绊倒了。}

\entry{punch}{出拳}{v. n.}{When you're throwing so many punches, it's easy to lose your balance. 你在连续出拳的时候，确实很容易失去平衡。}

\entry{mascot}{吉祥物}{n.}{Well, when I came to again, they were giving our mascot, Loggy, an Indian burn. 我又来的时候，他们正要拧我们的吉祥物木木的胳膊。}

\entry{machete}{弯道}{n.}{That's when I pulled out my dad's machete. 正是那时我抽出了我爸的弯刀。}

\entry{graze}{擦伤}{v. n.}{It grazed my arm, but I recovered. 我的手臂擦伤了，但是我后来好了。}

\entry{birthmark}{胎记}{n.}{It's like a birthmark on a chain. 简直就是链子上的胎记啊。}

\entry{pitch in}{投入}{}{They need the student body to pitch in. 他们只能让学生也出点力。}


\end{multicols}