\section{S01E12 Dribbling Bounce Tiger Pass Dragon}

\begin{multicols}{2}
    
\entry{macaroni}{通心粉}{n.}{I'm just afraid that macaroni art could be offensive to our "I-talian" Families. 我只是担心通心粉作品会冒犯我们的意大利家庭。}

\entry{quesadilla}{墨西哥烧饼}{n.}{Where'd you get quesadillas? 你们哪儿弄来的墨西哥烤饼。}

\entry{nerdy}{令人厌烦的}{adj.}{Maybe if there's a nerdy friend or a magical thing where someone wanders into a Chinatown, but no. 或许如果有个怪胎朋友或是发生了奇迹有人进入了唐人街，但那是不可能的}

\entry{goggle}{护目镜}{n.}{I told you, Doug, I'm the goggle guy. 我告诉过你，道格，我才是目镜哥。}

\entry{persuit}{职业}{n.}{My mother was supportive of my creative pursuits. 我我母亲很支持我的创作。}

\entry{fabric}{布}{n.}{We don't need all the extra, fabric getting in the way of our footwork. 我们不用那么长，多余的布料会妨碍步法的。}

\entry{bleach}{漂白（剂）}{v. n.}{And white. Looks like someone bleached a chost. 而且很白，像有人把幽灵漂白了似的。}

\entry{bald}{秃顶（的）}{v. adj.}{But he's already balding. 可他已经开始秃顶了。}

\entry{gum}{口香糖；牙龈}{n.}{They think life is all gumdrops and warm hugs. 他们以为生活满是橡皮软糖和温暖的拥抱。}

\entry{towel}{毛巾；用毛巾擦}{n. v.}{Ball? Towel? Sports drink? 球，毛巾，还是运动饮料？}

\entry{goof}{打发时间}{v.}{Okay, boys, enough goofing off! 伙计们，别吊儿郎当了。}

\entry{lame}{瘸的}{adj.}{Oh, you think drills are lame? 觉得常规练习没用是吗。}

\entry{improvisation}{即兴作品}{n.}{He may play for the Jazz, but there's no improvisation in his game. 或许他效力于爵土队，但比赛时他的表现全靠平时积累。}

\entry{dunk}{浸入}{v.}{Yeah, we caught that lesson five dunks ago. 是啊，在5次灌篮前我们就学到这一课了。}

\entry{substance}{物质}{n.}{Substance over style. 实质要胜过耍酷。}

\entry{ragtag}{bum}{n.}{They were a band of ragtag misfits from all corners of town. 有一队怎么看都不协调的乌合之众。}

\entry{bum}{流浪汉；乞讨}{n. v.}{Just as I thought. This bum-drop hasn't worked in months. 跟我想的一样，这流浪汉都几个月没工作了。}

\entry{lisp}{口齿不清}{n. v.}{Unicorn girl with a lisp! Was it you? 大舌头独角女，是你吗？}

\entry{spank}{拍打}{v. n.}{Speaking from experience, that was a spanking. 从经验来看，他们刚刚真是太赞了。}

\entry{foul}{犯规}{n. v.}{Foul! 犯规。}

\entry{gutter}{贫民区}{n.}{And not end up in the gutter, with a low credit rating like Mr. Gumdrop. 避免沦落到贫民区，信用评级像橡皮糖先生那么低。}

\entry{brittle}{脆弱的}{adj.}{I deserved a little horse, with brittle hair to comb and braid and a human face to kiss at night. 一匹小马是我应得的，我可以梳她的硬鬃毛，还可以编辫子，她有人脸，我可以在睡前吻一下。}

\entry{braid}{辫子；编辫子}{n. v.}{I deserved a little horse, with brittle hair to comb and braid and a human face to kiss at night. 一匹小马是我应得的，我可以梳她的硬鬃毛，还可以编辫子，她有人脸，我可以在睡前吻一下。}


\end{multicols}