\section{S02E01 全家出差之行}

\begin{multicols}{2}

\entry{stoked}{振奋的}{adj.}{So stoked for high school, to spend the summer with my mom. 要上高中非常开心，我要和我妈一起度过这个夏天。}

\entry{janitor}{看门人}{n.}{Or we'll be stuck eating lunch with the janitor all year. 不然我们整年就只能和看门人一起吃午餐。}

\entry{fairy}{仙女}{n.}{Oh, looks like it's time for another visit
from the tooth fairy. 哦，看来牙仙子又要再次造访了。}

\entry{criticism}{批判，评论}{n.}{I look forward to the fairy's constructive criticism. 我好期待牙仙子的建设性意见。}

\entry{Velcro}{维可牢}{n.}{No more Velcro. You're old enough for laces now. 不能再穿魔术贴的鞋了。你到了穿绑带鞋的年龄了。}

\entry{suspenders}{背带}{n.}{Jessica, I can't find my suspenders. 杰西卡，我找不到背带了。}

\entry{misery}{痛苦，《危情十日》}{n.}{White wine and Misery!  白葡萄酒和《危情十日》。}

\entry{piss}{小便，撒尿弄脏}{n. v.}{ }

\entry{pissed}{醉}{adj.}{Don't be pissed. 别喝醉了。}

\entry{franchise}{专营权}{n.}{National franchise convention... Biggest in central Florida. 全国加盟商大会，弗洛里达州中部最大的会议。}

\entry{alligator}{短吻鳄}{n.}{Gator World, the home of the scariest ride
in Florida, the Death Roll? 短吻鳄时间，弗洛里达恐怖游乐设施的发源地，还有死亡翻滚。}

\entry{bump}{肿块，碰撞}{n. v.}{Jumpin', bumpin', thrivin' gators. 跳吧，撞吧，强壮的短吻鳄。}

\entry{drown}{淹没，淹死}{v.}{You better swim, or you might drown. 你最好会游泳，不然可能会淹死。}

\entry{floss}{牙线，用牙线}{n. v.}{That's my key to flossin' through 7th grade. 这是我度过七年级的关键。}

\entry{soar}{高飞，猛增}{v.}{Off 1-4, Gator World, come and soar. 1到4，短吻鳄世界，快来玩吧。}

\entry{breach}{缺口，破坏}{n. v.}{Data breach. Clear identity theft. 这是数据泄露，很明显是身份盗窃。}

\entry{chomp}{切齿}{v.}{Now, we can go now. Chomp, chomp, Gator World. 我们现在就走。快点，快点，去短吻鳄世界。}

\entry{inflated}{天价的，夸大的}{adj.}{What kind of sucker would pay those inflated prices? 哪种冤大头会买这种天价票啊？}

\entry{upholstery}{家居装饰业}{n.}{-The upholstery seminars in Montreal? -Oui. 蒙特利尔的家居装饰研讨会？是的。}

\entry{rein}{缰绳}{n.}{You can loosen the reins a little. We'll be fine. 你也可以去稍微放松一下。}

\entry{splurge}{挥霍}{v.}{We splurge a bit? Spend a little money? We can afford to. 我们挥霍了吗？花了点钱吗？我们付得起的。}

\entry{preach}{劝诫}{v.}{Preach it, big man. 说多点，男子汉。}

\entry{marinate}{腌制}{v.}{I could be marinating meat or driving. 我可以去腌点肉或者开开车。}

\entry{hump}{大隆起物}{n.}{No, it's an underwater recording of humpback whales singing. 不是，只是座头鲸唱歌的水下录音带。}

\entry{resort}{度假胜地}{n.}{"A-Additional occupancy fee, resort fee, share fee"? 额外入住费，度假费，分担费？}

\entry{disfigurement}{毁容}{n.}{Your bill didn't include my child-disfigurement fee. 账单里也没有我孩子的毁容费啊。}

\entry{harpoon}{鱼叉}{n.}{-I grabbed my harpoon... -Dude, that's, like, a baby tooth. 我拿起鱼叉…… 老兄，那是一颗乳牙。}

\entry{blow off}{失约}{undefined}{Partied too much with my mom and blew off summer school. 和我妈去太多派对了，没上暑假班。}



\end{multicols}
