\section{S02E02 男孩·男人乐队}

\begin{multicols}{2}

\entry{elective}{选修的，选修课}{adj. n.}{School's giving you a choice of activities
for your fifth-period elective. 学校给了份第五节选修课的活动清单。}

\entry{piccolo}{短笛}{n.}{-I chose piccolo. -Piccolo? But I wanted leatherwork! 我选了短笛。短笛？可是我想学皮革制作。}

\entry{saddle}{马鞍}{n.}{I was gonna craft myself a pair of Timbos or maybe a saddle. 我想给自己做一双靴子或者马鞍。}

\entry{plum}{李子}{n.}{Anyway, that's how my mom tried to sell me on plums. 反正我妈就是这样让我吃李子的。}

\entry{dumb}{愚蠢的，说不出话的}{adj.}{I picked on them last year when they were all dumb 7th graders. 那时他们还都是七年级的傻蛋。}

\entry{clown}{小丑}{n.}{You clown jockeys looking at something? 你们这帮小丑在看什么？}

\entry{criticize}{评论}{v.}{All you have to do is day-drink and criticize her weight. 你只要每天喝个烂醉，然后抨击她的体重就好了。}

\entry{obsessed}{着迷的，着迷}{adj. v.}{Why are Americans so obsessed with being friends with their children? 为什么美国人这么执着和他们的孩子做朋友呢？}

\entry{pawn}{小兵}{n.}{Children are the pawns, and you are the queen. 孩子是小兵，而你是皇后。}

\entry{dope}{酷毙了}{adj.}{Yeah. That could be dope. 对哦，这还挺酷的。}

\entry{ravioli}{意大利饺子}{n.}{You better not be going into the kitchen to eat ravioli! 你最好别去厨房吃意大利饺子。}

\entry{extravagant}{奢侈的}{adj.}{You called me "sweetie," so you probably want something extravagant 你叫我小甜甜，所以你可能想要很旺贵的东西。}

\entry{buckle}{带扣}{n.}{One with a buckle and a strap. 纽扣绑带鞋呢。}

\entry{strap}{皮带}{n.}{One with a buckle and a strap. 纽扣绑带鞋呢。}

\entry{gambit}{开场白}{n.}{In my opening gambit. 在我的开局赌局中。}

\entry{outmaneuver}{智取}{v.}{I need to outmaneuver him. 我要智取他。}

\entry{hormones}{荷尔蒙}{n.}{I'm sure it's hormones. 我确定是荷尔蒙在作怪。}

\entry{mortgage}{抵押借款}{n.}{You know, when the mortgage is due. 你们知道的，到还款日了。}

\entry{invincible}{不可战胜的}{adj.}{-We're invincible. -My boy's in a history dress! 我们所向披靡啊。我兄弟穿了条古董裙。}

\entry{freaky}{畸形的}{adj.}{I think it's freaky! 我觉得这很奇怪。}

\entry{curse}{诅咒}{n.}{It's like a curse! 像个诅咒一样。}

\entry{peck}{啄}{v.}{So this poor cabbage baby is left alone in the fields to be pecked at by crows. 那么这个可怜的卷心菜宝宝就被留在这等着被乌鸦啄食。}

\entry{hamster}{仓鼠}{n.}{I finally finished it! This is why we flush our hamsters. 我终于看完啦！这就是为啥我们得处理掉仓鼠。}

\entry{scrawny}{骨瘦如柴的}{adj.}{He has Dave, uh, the scrawny one... 那个瘦竹竿大卫。}

\entry{devastated}{极为震惊的}{adj.}{When Oscar Chow dumped me in college... I was devastated. 当时奥斯卡·周在大学里甩了我，那时我都崩溃了。}



\end{multicols}
