\section{S02E03 沙奎尔·奥尼尔汽车}

\begin{multicols}{2}

\entry{condo}{公寓}{n.}{Okay, so, I'll drop you off at work, go to the dry-cleaners, and then take the Robertsons to go see some condos. 先到你的餐馆，我再去拿干洗的衣服，然后带罗伯森一家去看公寓。}

\entry{linen}{亚麻布}{n.}{12 years... the silk and linen anniversary. 第十二年是亚麻婚。}

\entry{wilt}{枯萎}{n. v.}{Why do I want to watch money wilt? 我怎么会愿意看到一束钱凋谢？}

\entry{glamorous}{迷人的}{adj.}{Don't worry. You guys will be nice and cool in the air-conditioned luxury of this glamorous baby... a brand-new 1995 Honda Accord in champagne pearl, the most elegant color in the neutral rainbow. 别担心，你们也会又帅又酷。这辆1995年出的全新豪华版香槟珍珠色雅阁光彩夺目，装有空调。这是纯色中最优雅的颜色。}

\entry{bunch}{串，使成一串}{n. v.}{They paid The Diesel a bunch of money
to slap his name on something. 他们给汽车公司一笔钱，把他的名字涂在某个地方。}

\entry{slap}{掌击，直接地}{n. v. adv.}{They paid The Diesel a bunch of money
to slap his name on something. 他们给汽车公司一笔钱，把他的名字涂在某个地方。}

\entry{funyuns}{洋葱圈}{n.}{Some old Funyuns. 只是些洋葱圈屑。}

\entry{tatter}{毁坏，破布条}{v. n.}{I collect them. I have all of these, except that boring-looking unicorn with the tattered label. 我收集了，这些我都有，除了那只标签破了的无聊独角兽。}

\entry{testicles}{睾丸}{n.}{-This set of testicles bothering you? -No, Deb. He's just my husband. 这个臭男人是不是在骚扰你？没，呆逼，他是我老公。}

\entry{tangle}{乱糟糟的一对，使乱成一团}{n. v.}{You'll be able to tell your firstborn that you tangled with the best. 将来你可以告诉你的长子你曾经和高手过过招。}

\entry{weld}{焊接}{n.}{I sat in the back with her welding equipment. 我和她的焊接器一起坐在后座。}

\entry{luster}{光泽，使有光泽}{n. v.}{The neutral luster is so elegant. 纯色光泽这么高贵。}

\entry{remorse}{懊悔}{n.}{Returner's remorse. 退货的顾客反悔了。}

\entry{shred}{碎片，撕碎}{n. v.}{So, you know what? I won't shred this check you gave me, -and we'll just... 您知道么？我不会撕掉这张你给我的支票。}

\entry{meditate}{冥想}{v.}{I'm so mad at you, Eddie. I have to go meditate. 我对你真生气，艾迪。我要去冥想了。}

\entry{snore}{打呼噜，呼噜}{v. n.}{Good morning, sleepy head. -You were snoring. 早上好，贪睡的大头鬼。你在打鼾。}

\entry{freak}{怪物}{n.}{So either you're a neat freak. 所以要么你是个洁癖狂。}

\entry{stain}{被玷污，污点}{v. n.}{which I know you're not by the salsa stains on your shirt. 因为你衬衫上还有莎莎酱。}

\entry{wunderkind}{天才}{n.}{What can I say? I'm a wunderkind who likes wet burritos. 我能说啥？一个喜欢多酱卷饼的天才。}

\entry{tequila}{龙舌兰酒}{n.}{-Shaq-uila. -Nice. basketball-shaped tequila. 鲨舌兰酒。很不错啊，篮球形的龙舌兰。}

\entry{autograph}{亲笔签名}{n.}{-You got Shaq's autograph? -On his big shoe. 你拿到了大鲨鱼的亲笔签名？还是签在他的大球鞋上。}

\entry{raccoon}{浣熊}{n.}{Some raccoons got into the Corollas. 一些浣熊跑到花冠车里去了。}

\entry{corolla}{花冠}{n.}{Some raccoons got into the Corollas. 一些浣熊跑到花冠车里去了。}

\entry{garage}{车库}{n.}{Out there, there are 387 more new and pre-owned cars, each one of them looking for a warm garage to call home. 在外面停着387辆新车和二手车，每辆车都等待着一个温暖的主人把它领回家。}

\entry{embroider}{绣花}{v.}{Remember the name that's embroidered on the front of your shirts... Shaquille... 记住绣在你们工作服前面的名字：沙奎尔}




\end{multicols}
