\section{S02E04 秋季舞会}

\begin{multicols}{2}

\entry{flipping}{非常}{adj. adv.}{House flipping... That's where the real money is. 炒房……钱就是这么来的。}

\entry{renovate}{翻新}{v.}{I just finished renovating our house. 我的房子刚刚翻新好。}

\entry{mural}{壁画，墙壁的}{n. adj.}{Erased all memories of Marvin's ex, minus her wall murals, which are actually quite beautiful. 抹去了马尔文前妻的所有痕迹，除了她的壁画，其实还蛮漂亮的。}

\entry{stray}{在歧途的，走失}{adj. v.}{You found the stray dog that gets into our freezer? 你找到钻进我们冰柜的流浪狗了？}

\entry{mellow}{熟透的}{adj.}{She will, too. She's mellowing out. 她也会的，她放松了。}

\entry{profoundly}{深深地}{adv.}{It is news that will affect each and every one of you profoundly. 这条新闻会对你们每个人有很深的影响。}

\entry{chaperone}{监护，监护人}{v. n.}{So, we're asking parents if they can help out at The Fall Ball by donating food or chaperoning. 我们想问一下家长能否为秋季舞会捐些食物或者陪着孩子一起参加。}

\entry{morale}{士气}{n.}{To keep morale up, they would play John Hughes movies on the VCR. 为了让我们保持干劲，他们经常播放约翰·休斯的电影。}

\entry{eavesdrop}{偷听}{v.}{All right, I've been eavesdropping, and this is not worth missing frozen yogurt for. 行了，我一直在偷听你们说话，这种谈话不值得你错过冰冻酸奶。}

\entry{grind}{磨碎}{v.}{We've been watching The Grind on MTV. 我们一直在看MTV的《扭动》。}

\entry{gyrate}{旋转}{v.}{'Cause we're gonna gyrate them into our orbit. 我会把她们都带进来。}

\entry{classy}{上等的}{adj.}{She sends her used pogs to Africa. She's classy. 她把玩过的游戏光盘寄到非洲。她很漂亮。}

\entry{repurpose}{轻微改动}{v.}{He meant it as a fighting move, but I repurposed it. 他教的是武术，但我改进了一下。}

\entry{sneeze}{喷嚏，打喷嚏}{n. v.}{He was the reason I put a sneeze guard
on the salad bar. 我在沙拉台上放个喷嚏罩就是因为他。}

\entry{gulf}{隔阂，海湾，吞没}{n. v.}{She'll just ask me why you didn't ask her
and the gulf between you will grow. 她会说为什么你不直接问她，你们之间的隔阂会加深。}

\entry{all of a sudden}{突然}{}{Wow, so busy all of a sudden. 哇哦，怎么突然这么忙了啊。}

\entry{fountain}{喷泉}{n.}{You take coins out of the fountain? 你要把硬币从喷泉里拿出来？}

\entry{frosted}{冻伤的，下霜}{adj. v.}{But I got frosted tips. 可我已经弄成杀马特了。}

\entry{tinfoil}{锡纸}{n.}{He asked for the premium tinfoil. 他可是要求用顶级锡纸。}

\entry{lean}{倾斜}{v. n.}{Figure we'll lean up against a wall and see what's what. 我想我们会靠着墙，然后看看做点什么。}

\entry{elbows}{用肘推}{v.}{Boy meets girl, boy falls in love, girl elbows boy in the ribs. 男孩遇见女孩，男孩爱上女孩，女孩推开男孩。}



\end{multicols}
