\section{S02E05 死亡街的奇迹}

\begin{multicols}{2}


\entry{}{}{undefined}{Man, I wouldn't fight me. 天啊，太酷帅了。}

\entry{aloe vera}{芦荟}{n.}{She planted aloe vera in it. 她拿去种芦荟了。}

\entry{termite}{白蚁}{n.}{I also suggest spraying for termites before you list the house. 我也建议你在登记房子之前喷一些除蚁喷雾。}

\entry{blast}{猛攻，爆炸}{v. n.}{That's how you blast your biceps, Louis. 这样能练练你的二头肌，路易斯。}

\entry{bicep}{肱二头肌}{n.}{That's how you blast your biceps, Louis. 这样能练练你的二头肌，路易斯。}

\entry{porch}{走廊}{n.}{We're meeting tonight to discuss how early we should all turn off our porch lights. 我们应该多早熄掉门廊灯，然后赶过去。}

\entry{illusion}{假象}{n.}{I but a Chiquita sticker on the banana
to help sell the illusion. 我在香蕉上贴了金吉达贴纸，让它看起来像真的一样。}

\entry{genital}{生殖器的}{adj.}{Yeah, I'm pretty sure that drawing is something much more... genital. 这幅画更像是……生殖器。}

\entry{squirt}{喷出，喷湿，喷射}{v. n.}{It's clearly squirting fuel out of the top of... 它还在喷射燃料呢，就在顶端那……}

\entry{smack}{掌掴，拍}{n. v.}{Time for some smacks. 是时候教训教训他们了。}

\entry{prank}{恶作剧}{n.}{Oh, come on. It's Halloween! Kids play silly pranks every year. 拜托，那是万圣节啊，孩子们每年都会玩那些愚蠢的恶作剧。}

\entry{psych}{使紧张}{v.}{You psyched for Halloween? They let me out of the sewers. 万圣节快到了，激动吗？}

\entry{ransack}{洗劫}{v.}{So, as predicted, our community garden
was ransacked by squirrels. 不出所料，我们的社区花园遭到松鼠洗劫。}

\entry{countmeasure}{对策}{n.}{I urge us to replant with the defensive countermeasures I suggested the first time. 我强烈要求我们按照我第一次提议的对策重新种植。}

\entry{ruthless}{无情的}{adj.}{}

\entry{vigilant}{警惕的}{adj.}{They are ruthless and precise, vigilant and wise. 它们冷酷无情，又精准无误。}

\entry{nepotism}{裙带关系}{n.}{Nepotism! 裙带关系！}

\entry{booze}{酒}{n.}{We're gonna spend Halloween hanging in the park and seeing if anyone can buy us booze. 我们打算在公园里度过万圣节，看看有没有人请我们喝酒。}

\entry{toddler}{小孩}{n.}{We got five hours before the first toddler wave hits. 在第一波孩子到来之前，我们还有五个小时。}

\entry{rotten}{腐烂的}{adj.}{We bought our supply weeks ago. They're nice and rotten by now. 我们几个星期之前就装备好了，它们现在已经乖乖腐烂了。}

\entry{scrap}{废弃}{v.}{Jordy scraped his knee picking up his skateboard. 乔迪在捡滑板的时候擦伤了膝盖。}

\entry{goalie}{守门员}{n.}{Nice costume, Emery. You too, Evan... a lazy goalie. 服装不错，艾默里。你也是，艾文，一个懒散的守门员。}

\entry{tomfoolery}{愚蠢的行为}{n.}{That's just some fright night tomfoolery. 只是一些惊恐之夜的恶作剧。}

\entry{raisin}{葡萄干}{n.}{How come I keep getting stuck with mini boxes of raisins? 为什么我总是得到小盒葡萄干？}

\entry{mayhem}{大混乱}{n.}{One is filled with cute costumes and candy, and the other is built on chaos and mayhem. 一种是充满可爱的服装和糖果，另一种则是混乱和破坏。}

\entry{hose}{冲洗，软管}{v. n.}{I catch the egg, I hose them down. 我能接住鸡蛋，把它们冲下去。}

\entry{yardstick}{工程尺子}{n.}{I'm sorry. My yardstick got caught in the handle. 抱歉，我的尺子卡在把手里了。}

\entry{wig}{假发}{n.}{Remember? The wig I bought you with the bow? 还记得吗，我为你买的假发？}

\entry{punk}{小混混，低劣的}{n. adj.}{We need to figure out a way to scare those punks so badly, they'll never come back. 我们要想一个办法吓死那些小混混。}

\entry{tampon}{卫生棉塞}{n.}{What are you tampons dressed as? 你们这些浑小子又是装扮成谁啊。}

\entry{scrote}{混蛋}{n.}{You scrotes think you're fooling anyone
with those clip-on ties? 你们这些混蛋想用假领带糊弄谁？}

\entry{warrior}{战士}{n.}{Did you know his hairstyle actually honors his African warrior heritage? 你知道吗，他的发型实际上是为了纪念非洲传统。}


\end{multicols}
