\section{S02E06 早上好奥兰多}

\begin{multicols}{2}

\entry{bracelet}{手镯}{n.}{Sarah S. slapped a slap bracelet on me at the dance. 萨拉跳舞的时候手镯甩到了我。}

\entry{riddle}{使布满孔洞，谜}{v. n.}{I bought an investment property which, it turns out, is riddled with termites. 我买了一栋房子用来投资，结果房子里白蚁泛滥。}

\entry{celebrity}{名人}{n.}{They're celebrities from television. 他们是电视上的名人。}

\entry{prostitution}{卖淫}{n.}{I mean, as customers, not... we don't encourage prostitution. 我是说作为顾客，欢迎他们来。我们不鼓励卖淫。}

\entry{sting}{讽刺，刺激}{n.}{Is this a sting? Because you have to show me your badge if I ask you. 这是圈套吗？请你们出示你们的证件。}

\entry{trickle}{滴}{v.}{Guess you guys got my overflow... trickle down love-onomics. 你们一定感受到我溢出来的爱了吧。}

\entry{escalator}{自动扶梯}{n.}{The mall, today, 3:00, by the escalators. 商场，今天，三点，自动扶梯那里。}

\entry{hullabaloo}{喧嚣}{n.}{A hullabaloo was caused this morning. 今天早上发生一些骚乱}

\entry{hash browns}{洋葱土豆煎饼}{n.}{I need hash browns! 我要我的土豆煎饼！}

\entry{clown}{扮小丑，小丑}{v. n.}{That's why when we do, we need to present our best face... not clown around, like you did today. 因此有这种机会时，我们要呈现出最好的一面。而不是像昨天那样扮小丑。}

\entry{cab}{出租车，乘出租车}{n. v.}{Oh, here comes a cab. 来了一辆出租车。}

\entry{hilarious}{滑稽的}{adj.}{Hey, we saw you on Good Morning Orlando.Hilarious! 我们在《早安奥兰多》上看到你了，很有趣。}

\entry{veal}{小牛肉}{n.}{I ordered the veal. 我点了小牛肉。}

\entry{platonic}{柏拉图哲学的，不切实际的，理想的}{adj.}{So, Alison pushed us all in the mosh pit, but were those pushes platonic
or passionate? 这么说，艾莉森，在舞池推了我们所有人。但是她对谁的感情是认真的呢？}

\entry{inconclusive}{非决定性的}{adj.}{Evidence is inconclusive. 还没有确切证据表明。}

\entry{roller rink}{溜冰场}{n.}{But the girls do want to have another group date at the roller rink tomorrow. 但是她们明天想去滑冰场，再来一次集体约会。}

\entry{ bust}{爆裂，使破产}{v.}{They'll bust us wide open, and then none of us will have girlfriends. 他们会把我们打得落花流水，那谁都别想有女朋友了。}

\entry{infertile}{不育的}{adj.}{Apparently, human touch would render
the endangered tortoise infertile. 很明显，人类的接触会使这种濒危乌龟不育。}

\entry{heck}{表吃惊}{int.}{What the heck is going on here? 这到底是怎么一回事？}

\entry{shrubbery}{灌木，灌木丛}{n.}{Breaking news...another tortoise has appeared in the shrubbery... 重大消息，又有一只乌龟出现在灌木丛里。}

\entry{barge}{冲，闯}{v.}{Sorry to barge in like this, but they banned me from the studio. 很抱歉打断你们，但是他们禁止我进入演播厅。}

\entry{screw}{拧}{v.}{I screwed things up with Alison. 我搞砸了我和艾莉森的关系。}



\end{multicols}
