\section{S02E07 大大的十二岁}

\begin{multicols}{2}

\entry{bunchy}{成串的，束状的}{adj.}{I don't like it when the ends get bunchy. 边角皱了我就不喜欢了。}

\entry{fiesta}{节日}{n.}{Mm, I think it's finally time we send him to the big fiesta in the sky. 我想是时候送他个大的生日派对了。}

\entry{pedophiled}{恋童癖者}{n.}{You will thank me when you don't get pedophiled. 等你没有恋童癖的时候你会感谢我的。}

\entry{streamer}{彩带}{n.}{Where are all the streamers and scallion pancakes and birthday hats? 那些彩带和葱油饼都到哪里去了，还有生日帽呢？}

\entry{odorless}{无臭的}{adj.}{An odorless gas for a bug you can't see?
Smart scam. 一种你看不见的臭虫的无味气体？聪明的骗局。}

\entry{tater tots}{炸薯球}{n.}{Last year, Nicole said that she wanted to eat tater tots and watch TV for her birthday. 去年，妮可说她生日的时候想吃炸土豆，看电视。}

\entry{patio}{露台，天井}{n.}{so that way, I could secure the patio. 这样，我可以留下这个露台。}

\entry{boobs}{乳房}{n.}{Shirt boobs. 衬衫乳房。}

\entry{preservatives}{防腐剂}{n.}{You said you wouldn't buy those because preservatives make you go blind. 你说过你不会买的，因为防腐剂会让人失明。}

\entry{stool}{凳子}{n.}{Honey, do you have a stool? 亲爱的，有凳子吗？}

\entry{fatality}{死亡}{n.}{Fatality. 死亡。}

\entry{spine}{脊椎}{n.}{Dude, you just ripped my spine out of my back. 兄弟，你把我的脊梁骨都扯下来了。}

\entry{spoil}{毁坏，变质}{v.}{But wait. Aren't we gonna spoil our dinner? 等下，会不会影响我们的晚餐？}

\entry{brew}{酿造}{v.}{Not for long, though. Mama's got one brewing. 不过不持久，妈妈也憋一个。}

\entry{rub}{擦，摩擦}{v. n.}{Just rub it in. 擦一下就行了。}

\entry{chore}{家庭杂务}{n.}{you have to do your chores, you can't have a lizard. 你必须做你的家务，你不能养蜥蜴。}

\entry{fart}{放屁}{v.}{-What's weird about my house? -Dude, you fart on your mom! 我家有什么奇怪的？老兄，你朝你妈身上放屁。}

\entry{shrimp}{虾，捕虾，有虾的}{n. v. adj.}{Shrimp jumped off a skillet, got me right here. 虾从煎锅上跳了下来，留给我的疤痕。}

\entry{skillet}{煎锅}{n.}{Shrimp jumped off a skillet, got me right here. 虾从煎锅上跳了下来，留给我的疤痕。}

\entry{dementia}{痴呆}{n.}{An old man with dementia stabbed me on the street. 一个痴呆老人在街上捅了我。}

\entry{stab}{捅}{v. n.}{An old man with dementia stabbed me on the street. 一个痴呆老人在街上捅了我。}


\end{multicols}
