\section{S02E08 黄家感恩节}

\begin{multicols}{2}

\entry{crate}{板条箱}{n.}{I've been sending crates of these babies
to my mother for weeks. 我一直在给我妈送这些宝贝。}

\entry{charade}{你画我猜}{n.}{and Steve making everybody play charades. 史蒂夫还总让我们玩你画我猜。}

\entry{mime}{比划，表演哑剧，哑剧}{v. n.}{He was just miming a big Afro. 他就比划了一个爆炸头。}

\entry{hoedown}{民间舞会}{n.}{-The theme... "Harvest hoedown." -Or "Polar bear pilgrims." 主题”收获季“，或者北极熊朝圣者。}

\entry{pilgrim}{朝圣者}{n.}{-The theme... "Harvest hoedown." -Or "Polar bear pilgrims." 主题”收获季“，或者北极熊朝圣者。}

\entry{measly}{不足的，很小的}{n.}{Second, aren't you sick of having to fight over one measly roast duck
at Steve and Connie's? 在他们家，所有人都抢一只烤鸭，还少得可怜。你们肯定不喜欢这样吧？}

\entry{beak}{鸟嘴}{n.}{Last year, I got the beak. 去年我只吃到了鸭嘴。}

\entry{}{}{undefined}{Get ahold of yourself, Steve. Nobody wants to see this. 省省吧，史蒂夫，没人想看你表演。}

\entry{hay}{干草}{n.}{We had them sharing a love seat made of hay! 我们给他们准备了干草铺得情侣位呢。}

\entry{whisker}{胡须}{n.}{Oh, I see some whiskers. 我看见胡须了。}

\entry{tabby}{虎斑猫}{n.}{Could it be everybody's favorite tabby? 这不是人见人爱的虎斑猫吗？}

\entry{sabotage}{破坏}{v. n.}{I bet this is all part of Steve and Connie's plan to sabotage our Thanksgiving! 我打赌这是史蒂夫和康妮的诡计，就是为了破坏我们的感恩节。}

\entry{hang over}{宿醉}{n.}{How are you not hung over? 你怎么没有宿醉后遗症啊？}

\entry{stingy}{小气的}{adj.}{Cranberries... very stingy berry. 蔓越莓是非常小气的莓子。}

\entry{brine}{用盐水浸泡，卤水}{v. n.}{I'll have them brined, roasted, and on the table by 6:00 p.m. 我会把鸡肉腌好，六点上餐桌。}

\entry{hiccup}{小问题，嗝}{n.}{This is a slight hiccup. That's all. 这只是个小插曲，没关系的。}

\entry{gussy}{装饰}{n.}{We want to gussy up the gourds. 我们想把葫芦挂起来。}

\entry{gourd}{葫芦}{n.}{We want to gussy up the gourds. 我们想把葫芦挂起来。}

\entry{amputate}{截肢}{v.}{It was frozen to a tub of mayonnaise, so I had to amputate. 当时还是冰的，粘在一桶蛋黄酱上了。所以我给它截了个肢。}

\entry{stump}{残余部分}{n.}{I'll cover the stump with a yam. Let's put it in the oven. 我拿番薯盖住切掉的地方，把伙计放烤箱里吧。}

\entry{yam}{薯类}{n.}{I'll cover the stump with a yam. Let's put it in the oven. 我拿番薯盖住切掉的地方，把伙计放烤箱里吧。}

\entry{tote}{大手提袋}{n.}{Michael listens to NPR. Show her your tote. 迈克尔听美国国家广播电台的，给她看看你的包。}

\entry{relive}{再体验}{v.}{I thought we could eat it and relive our memories of Thanksgivings past. 我觉得我们可以尝尝，回忆过去的感恩节。}

\entry{acorn}{橡子}{n.}{-Why is this acorn here? -I think it brings a rustic quality. 这个橡子怎么在这里？我觉得它给人的感觉很淳朴。}

\entry{rustic}{淳朴的}{v.}{-Why is this acorn here? -I think it brings a rustic quality. 这个橡子怎么在这里？我觉得它给人的感觉很淳朴。}

\entry{lug}{拉着}{v.}{Is Louis ready to lug the leather? 路易斯准备好玩橄榄球了吗？}

\entry{carburetor}{汽化器}{n.}{I threw a carburetor across the stage as Kenickie in for two summer tours. 我演《油脂》里的肯尼基的时候，能把化油器从舞台一头扔道具另一头，整整两个暑假的时间。}

\entry{almond}{杏仁}{n.}{So, I was listening to the most fascinating story on NPR this morning about almonds. 我今早在美国国家广播电台听到一个引人入胜的故事，关于杏仁的。}

\entry{sensible}{明智的，敏感的人}{adj. n.}{Sensible vest. 马甲挺帅的。}

\entry{gridiron}{橄榄球场，格状物}{n.}{You got a great arm there, son. You belong on the gridiron. 你很强壮啊，老兄，你简直是铁人。}

\entry{repossessed}{收回}{n.}{No, thanks. It'll just get repossessed. 不用了，谢谢，反正也会被拿去抵债的。}

\entry{scoop}{抢先，小勺}{v.}{No way you're gonna swoop in and "rescue" my Thanksgiving. 我才不会让你来拯救我的感恩节呢。}

\entry{paralyzed}{瘫痪的}{adj.}{-My face was paralyzed for a year! -How convenient! 我的脸当时僵了一年好吗！你做得够碰巧的啊。}

\entry{bonnet}{软帽}{n.}{Honey's taking the bonnet off the gravy boat. 哈妮把酱汁盘的帽子拿下来了。}


\end{multicols}
